%-------------------------
% Resume in Latex
% Author : Akshay Shegaonkar Based off of: https://github.com/jakegut/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
    \item
        \small{#1}
}

\newcommand{\classesList}[4]{
    \item
        \small{{#1 #2 #3 #4 \vspace{-2pt}}}
}

\newcommand{\resumeSubheading}[3]{
    \item
        \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
        \textbf{#1}, \small{#2} & \textbf{\small #3}
        \end{tabular*}\vspace{-4pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
        \vspace{-2pt}
        \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
        \textit{\small#1} & \textit{\small #2}
        \end{tabular*}\vspace{-4pt}
}

\newcommand{\resumeProjectHeading}[1]{
    \item
        \begin{tabular*}{1.0\textwidth}{l@{\extracolsep{\fill}}r}
        \small#1\\
        \end{tabular*}\vspace{-4pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}}


%----RESUME STARTS HERE-----
\begin{document}
\begin{center}
    {\Huge\scshape Akshay Shegaonkar} \\ \vspace{1pt}
    \href{tel:+919595342495}{\raisebox{-0.2\height}\faPhone\ \underline{+91 9595342495}} ~
    \href{mailto:shegaonkar.akshay2@gmail.com}{\raisebox{-0.2\height}\faEnvelope\  \underline{shegaonkar.akshay2@gmail.com}} ~
    \href{https://www.linkedin.com/in/akkisdiary/}{\raisebox{-0.2\height}\faLinkedin\ \underline{linkedin.com/in/akkisdiary}} ~
    \href{https://github.com/akkisdiary}{\raisebox{-0.2\height}\faGithub\ \underline{github.com/akkisdiary}}
\end{center}

%-----------Technical SKILLS-----------
\section{Technical Skills}
\resumeItemListStart
    \resumeItem
    {\textbf{Languages}: Python, JavaScript, TypeScript, SQL, Shell Script, HTML, CSS, YAML}
    \resumeItem
    {\textbf{Tools \& Technologies}: AWS (EC2, EKS, S3, VPC), Kubernetes, Docker, Ansible, MySQL, MongoDB, Node.js, Terraform, Helm, Git, Github Workflows}
    \resumeItem
    {\textbf{Frameworks \& Libraries}: Flask, Pandas, NumPy, React JS, TailwindCSS}
\resumeItemListEnd


%-----------EXPERIENCE-----------
\section{Professional Experience}
\resumeSubHeadingListStart
    \resumeSubheading
    {Wiser Solutions, Inc.}{Pune, India}{July 2021 - Present}
    \resumeSubSubheading
    {Software Engineer 1}{Mar 2023 - Present}
    \resumeItemListStart
        \resumeItem
        {Enhanced and maintained a legacy \textbf{REST API} based data extraction platform, delivering \textbf{e-commerce data} to \textbf{Fortune 500} companies that enable clients to make informed business decisions, optimize their operations, and gain competitive market insights.}
        \resumeItem
        {Migrated the legacy extraction platform to a distributed architecture on \textbf{Amazon EKS} using \textbf{Kubernetes \& Docker}. Consolidated multiple sub-platforms into a single platform supporting various upstream systems capable of handling \textbf{200M+ traffic per day}.}
        \resumeItem
        {Resolved critical IP shortages within the \textbf{AWS VPC} by designing and implementing a new \textbf{Auto Scaling Group (ASG)} for extractor pods, unblocking project deployments and scaling.}
        \resumeItem
        {Developed multiple microservices to support the new architecture, streamlining the data extraction process and enhancing platform functionality with new \textbf{API endpoints}.}
        \resumeItem
        {Created a framework to convert \textbf{HTML documents into images}, now actively used by related teams in multiple bots reducing the \textbf{response times \& resource costs by 90\%}.}
        \resumeItem
        {Collaborated with multiple teams to migrate to \textbf{Coralogix}, enhancing monitoring and observability while \textbf{reducing costs}. Developed a solution to install telemetry agents in worker machines using \textbf{Ansible \& AWX}, providing customized configurations for various teams.}
        \resumeItem
        {Upgraded \textbf{Selenium grid} infrastructure to the latest Chrome version, improving compatibility and performance.}
        \resumeItem
        {Fixed and optimized \textbf{CI/CD pipelines} for various microservices, ensuring smooth deployment processes. Addressed and resolved multiple issues within the platform, enhancing stability and reliability.}
    \resumeItemListEnd
    
    \resumeSubSubheading
    {Associate Engineer}{Jul 2021 - Mar 2023}
    \resumeItemListStart
        \resumeItem
        {Develop \textbf{50+ Web Scraping} bots \& automated scripts using \textbf{Python} and \textbf{LXML HTML Parser,} capable of providing zip-code specific information.}
        \resumeItem
        {Advised and implemented a reusable framework for sending web requests using the \textbf{HTTP/2} protocol to bypass bot detection techniques, \textbf{improving the success rate by 95\%.} and reducing the dependence on expensive resources.}
        \resumeItem
        {Developed techniques to bypass popular bot detection techniques such as Cloudflare, Imperva, etc.}
        \resumeItem
        {Led the front-end development of an internal tool for monitoring Bots' performance using \textbf{React JS and TypeScript.} Using this tool we are able to quickly identify and resolve issues with bots before they are raised by clients thus ensuring accurate and reliable data.}
    \resumeItemListEnd

    \resumeSubheading
    {Mind Code Systems}{Pune, India}{Aug 2020 - Feb 2021}
    \resumeSubSubheading
    {Python Trainee}{Aug 2020 - Feb 2021}
        \resumeItemListStart
            \resumeItem
            {Developed \textbf{POC} for document management Web App using \textbf{Python, Flask, HTML, JavaScript and jQuery} supporting CRUD operations.}
            \resumeItem
            {Used \textbf{SQLAlchemy} to create models, queries \& connect to the \textbf{MySQL database} from the web server.}
            \resumeItem
            {Designed and implemented \textbf{data structure and algorithm} to replicate the File Hierarchy Structure using \textbf{OOPs principles}, supporting operations such as renaming, copying, moving and deleting. This allowed us to replicate the File Explorer UI in the front end.}
            \resumeItem
            {Collaborated with peers to deploy \textbf{ML model} on \textbf{Amazon EC2} and created \textbf{RESTful APIs} which provide automatic grammar correction.}
            \resumeItem
            {Implemented a User Authentication System and Help Desk Ticketing System with role-based access.}
        \resumeItemListEnd
\resumeSubHeadingListEnd


%-----------EDUCATION-----------
\section{Education}
\resumeSubHeadingListStart
    \resumeSubheading
    {DY Patil Institute of Engineering}{Pune}{June 2020}
    \resumeSubSubheading
    {Bachelor of Engineering in Computer Science (SGPA of 7.91)}{Pune, India}
\resumeSubHeadingListEnd


%-----------PROJECTS-----------
\section{Key Projects}
\resumeSubHeadingListStart
    \resumeProjectHeading
    {\textbf{Portfolio Allocation} $|$ Personal Project $|$ \href{https://github.com/Akkisdiary/portfolio-allocation}{Github \faExternalLink*} $|$ \href{https://portfolio-allocation.netlify.app/}{Live Link \faExternalLink*}}
        \resumeItemListStart
            \resumeItem
            {Techstack: \textbf{TypeScript, React JS, Python, Flask}}
            \resumeItem
            {Developed a \textbf{SPA} using \textbf{React JS} where users can visualize their \textbf{Stock Portfolio Allocation} by Industry, Sector, Exchange, Country and Currency.}
            \resumeItem
            {The user is able to search and add stock tickers from global markets with their live prices and update their holding quantity. Stock symbol and live prices are scraped using \textbf{Flask Restful Back-End} from \textit{TradingView.com}.}
        \resumeItemListEnd
        \resumeProjectHeading
        {\textbf{Secure Multi-Modal Summarization} $|$ Academic Project}
        \resumeItemListStart
            \resumeItem
            {Techstack: \textbf{Python, NLP, NLTK}}
            \resumeItem
            {Used the \textbf{LexRank Algorithm} derived from \textbf{Google's PageRank Algorithm} to create a system to extract a summary of a textual document. Multiple modes of information are supported like text, audio and video.}
            \resumeItem
            {Publish research paper on \href{https://drive.google.com/file/d/1Ik8ADmgQ161ozwnP4DED0riZerrP4JPw/view?usp=sharing}{\textbf{IJAERD Scientific Journal.} \faExternalLink*}}
        \resumeItemListEnd
\resumeSubHeadingListEnd


\section{Achievements}
\resumeItemListStart
    \resumeItem
    {Awarded \textbf{`Star Performer Award'} for the quarter ending \textbf{December 2023} at Wiser Solutions. \href{https://drive.google.com/file/d/11RvsYKlJ9UAnp2LHTLOc-FF-gGJzbBXb/view?usp=sharing}{\faExternalLink*}}
    \resumeItem
    {Awarded \textbf{`Star Performer Award'} for the quarter ending \textbf{September 2022} at Wiser Solutions. \href{https://drive.google.com/file/d/1SLFl3xMEQQykWYrRkAzT4aPqpjl47jUr/view?usp=share_link}{\faExternalLink*}}
    \resumeItem
    {Awarded \textbf{`Best Hack day Project (2022)'} at Wiser Solutions.}
    \resumeItem
    {Secured \textbf{1st rank} in district-level \textbf{Science Olympiad (2012)}.}
\resumeItemListEnd


\section{Certifications}
\resumeItemListStart
    \resumeItem
    {\textbf{IBM}: Machine Learning with Python. \href{https://drive.google.com/file/d/12Ia915pkCQcdrRhdlW5tJYu7HmfnpsRj/view?usp=sharing}{\faExternalLink*}}
    \resumeItem
    {\textbf{SkillUp Academy}: Foundation of Artificial Intelligence verified by NASSCOM Futureskills. \href{https://drive.google.com/file/d/1Y4Bm4yFah4c1AELEQ0Li6PR0jnRhj-1W/view?usp=sharing}{\faExternalLink*}}
\resumeItemListEnd
 

\end{document}
